--- 
title: "Mitos y verdades de las Elecciones Subnacionales en Perú"
author: Área de investigación e incidencia de la Escuela de Gobierno y Políticas Públicas
  - PUCP
date: 'Equipo de trabajo: Jorge Aragón, Marylía Cruz, Paolo Sanchez, Valeria Pinchi
  y Cinthya Villanueva'
site: bookdown::bookdown_site
documentclass: book
bibliography:
- book.bib
- packages.bib
description: |
  This is a minimal example of using the bookdown package to write a book.
  set in the _output.yml file.
  The HTML output format for this example is bookdown::gitbook,
link-citations: yes
github-repo: rstudio/bookdown-demo
---

# Presentación

El Área de Incidencia e Investigación de la EGPP- PUCP presenta “Mitos y verdades de las Elecciones Subnacionales en el Perú”, la cual tiene como objetivo presentar a detalle los principales mitos sobre los últimos seis procesos electorales subnacionales.

- Elecciones Regionales y Municipales 2002

- Elecciones Regionales y Municipales 2006

- Elecciones Regionales y Municipales 2010

- Elecciones Regionales y Municipales 2014

- Elecciones Regionales y Municipales 2018

- Elecciones Regionales y Municipales 2022


## Render book

You can render the HTML version of this example book without changing anything:

1. Find the **Build** pane in the RStudio IDE, and

1. Click on **Build Book**, then select your output format, or select "All formats" if you'd like to use multiple formats from the same book source files.

Or build the book from the R console:

```{r, eval=FALSE}
bookdown::render_book()
```

To render this example to PDF as a `bookdown::pdf_book`, you'll need to install XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.org/tinytex/>.

## Preview book

As you work, you may start a local server to live preview this HTML book. This preview will update as you edit the book when you save individual .Rmd files. You can start the server in a work session by using the RStudio add-in "Preview book", or from the R console:

```{r eval=FALSE}
bookdown::serve_book()
```


```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
